%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Tiffany Thu Olsen, G.I.T.} \\ \vspace{1pt}
    \small 832-729-0331 $|$ \href{mailto:tiffany.thu.olsen@gmail.com}{\underline{tiffany.thu.olsen@gmail.com}} $|$ 
    \href{https://www.linkedin.com/in/tiffanythuolsen/}{\underline{linkedin.com/in/tiffanythuolsen/}} 
  %  \href{https://github.com/...}{\underline{github.com/Stove2532}}
\end{center}
%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{The University of Alabama}{Tuscaloosa, AL}
{M.S. in Geology, GPA 4.0} {}
{}
\resumeItemListStart
\resumeItem
{Thesis: Reservoir Characterization of the Hartselle Sandstone in the Vicinity of Gorgas Power Plant, using Amplitude Variation with Offset (AVO). }
\resumeItemListEnd
\resumeSubheading
{Texas A\&M University}{College Station, TX}
{B.S. in Geophysics, Minors in Mathematics and Geology, GPA 3.6}{}
 \\



\resumeSubHeadingListEnd


%
\section{Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
	\small{\item{
		\textbf{Geologic skills:}{ Seismic interpretation, well log analysis, geological mapping, GIS (ESRI ArcGIS), geologic software (Petrel, Surfer, Hampson-Russell's GeoView, RoseRA) \\
				\textbf{Other skills}{: Programming (Python, Java, Javascript, and C), communication and presentation skills, bilingual (Vietnamese and English), Certifications (Harvard's CS50x Certificate, Geologist-In-Training Certificate)} \\
				

				\end{itemize}
				
				%--------------------


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Geologist I}{May. 2024 -- Present}
      {Geological Survey of Alabama}{Tuscaloosa, AL}
      \resumeItemListStart
        \resumeItem{Conducting research in geology and mineral, energy, and water resources of the state.}
     
              

        
        
      \resumeItemListEnd
 \resumeSubHeadingListEnd     
 
   \resumeSubHeadingListStart
 
 \resumeSubheading
 {Instructor of Geology, Lab Coordinator, Assistant Director of Outreach}{Aug. 2019 -- May 2024}
 {University of South Alabama}{Mobile, AL}
 \resumeItemListStart
 \resumeItem{Conducted geologic field work with the Unviersity of South Alabama professors and students during geology field course}
 
 \resumeItem{ Received the Teaching Excellence Award from the College of Art \& Sciences.}
 
 
 \resumeItem{Co-director of the Mobile Regional Science and Engineering Fair.}
  \resumeItem{Taught and coordinated geology labs.}
 
 \resumeItem{Delivered presentations on various topics and oversaw the geology booth at recruiting events.}
 
 
 
 
 
 \resumeItemListEnd
 \resumeSubHeadingListEnd     
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------
  \resumeSubHeadingListStart
    \resumeSubheading
      {Staff Geologist}{Nov. 2018 --May 2019}
      {Larson \& Associates, Inc.}{Midland, TX}
      \resumeItemListStart
       \resumeItem{Conducted geologic field work and research on the geology and water resources of New Mexico and West Texas.}
              \resumeItem{Conducted 58-acre magnetometer survey to locate plugged and abandoned wellbores, processed and interpreted magnetic results. }
             \resumeItem{Prepared geological cross-sections, groundwater maps, and technical reports, interpreted laboratory analysis from media samples.}



    \resumeItemListEnd
     \resumeSubHeadingListEnd 
     
  \resumeSubHeadingListStart
    \resumeSubheading
{GIS Intern}{Summer 2018}
{Setld, Inc.}{Pearland, TX}
\resumeItemListStart
\resumeItem{Digitized 500+ miles of oil and gas pipelines locations using ArcGIS to improve data accuracy and support Setld's GIS/ BI product.}
\resumeItem{Developed Setld's North American data product by inputting oil and gas data into the company's proprietary model with a team. }

\resumeSubHeadingListEnd

\resumeSubheading
{Geophysics and Economic Evaluation Team Lead }{Spring 2017}
{AAPG's Imperial Barrel Award Competition}{Anadarko Office - Spring, TX}
\resumeItemListStart
\resumeItem{Conducted prospective basin analysis with graduate geoscience students, analyzing seismic and well log data to identify two prospects in the Taranaki Basin, NZ. Delivered a 25-minute presentation to judges.}
    \resumeItemListEnd





\resumeSubheading
{Student Technician}{Summer 2015}
{Handin Laboratory for Experimental Rock Deformation, Texas A\&M University}{College Station, TX}
\resumeItemListStart
\resumeItem{Conducted salt consolidation experiments to support research on salt rock deformation in rock mechanic labs
}
\resumeItem{	Performed thin section making and analyzed grain size distribution using Excel.}



\resumeItemListEnd
\resumeSubHeadingListEnd 


\end{document}
